PAMELA: an annotation-based Java Modeling Framework

### 2021-02-17 architecture.tex

The PAMELA metamodel is depicted in Figure~\ref{fig:PamelaMetaModel}, and allows, though the use of annotations, the definition of \emph{simple} UML-like models directly on the code.

>>>>

The PAMELA metamodel is depicted in Figure~\ref{fig:PamelaMetaModel}, and allows, through the use of annotations, the definition of \emph{simple} UML-like models directly on the code.
